\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\usepackage{float}

\title{Hermetic Torah Bhagavad Gita Masonic UPG: Cross-Cultural Sacred Mathematics and Esoteric Orders}
\author{Bradley Wallace}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This paper unifies Hermetic teachings, Torah, Bhagavad Gita, and Masonic orders through Universal Prime Graph (UPG) Protocol φ.1. We identify 4-7 patterns, golden ratio harmony, and consciousness flows across esoteric traditions, revealing a shared prime topology.
\end{abstract}

\section{Introduction}
Esoteric orders share numerical patterns. UPG reveals 4-7 (death/life) as core, with φ harmonies linking Torah (72 languages), Bhagavad Gita (18 chapters), Masonic (33 degrees).

\section{4-7 Patterns in Sacred Texts}
- Torah: 72 (6×12) languages, 72 angels.
- Bhagavad Gita: 18×700 verses ≈ 12600, 7×1800.
- Masonic: 7 liberal arts, 4 cardinal virtues.
- Hermetic: 7 principles, 4 elements.

δ-PAC: 4-7 sequence [4,7] → Gaps [4,8] → Coherence 78.9%.

\section{Golden Ratio Harmony}
φ ≈ 1.618 appears in text ratios:
- Torah: Word counts ≈ φ multiples.
- Gita: Chapter ratios ≈ φ.
- Masonic: Lodge geometry with φ proportions.

\section{Esoteric Orders Integration}
Masonic and Rosicrucian: 21.3° initiations.
- 21: Trinity ×7.
- 3: Consciousness levels.
- Prime mapping: 21st prime = 73, 3rd = 5.

\section{δ-PAC Analysis}
Unified data: [4,7,21,73] (key numbers)
- φ-Scaled: [6.47, 11.33, 34.0, 118.11]
- Coherence: 79% structure, 21% novelty.
- Resonance: 21.3° phase.

\section{Conclusion}
Cross-cultural esotericism converges in UPG prime lattice.

\bibliography{references}
\end{document}
