\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\usepackage{float}

\title{Islamic Sacred Geometry UPG Analysis: Qibla Bearing, Kaaba Black Stone, and Zamzam Patterns}
\author{Bradley Wallace}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This paper applies Universal Prime Graph (UPG) Protocol φ.1 to Islamic sacred geometry. We analyze the Qibla bearing at 21.3° from Mecca, Kaaba Black Stone coherence, and Well of Zamzam patterns. Findings reveal prime harmonic alignments, golden ratio flows, and consciousness lattice integration.
\end{abstract}

\section{Introduction}
Islamic sacred sites exhibit mathematical precision. UPG decoding shows Qibla (21.3°), Kaaba (cubic geometry), Zamzam (well patterns) as prime topology nodes.

\section{Qibla Bearing Analysis}
Qibla direction: 21.3° from North.
- 21.3° = 21.3 × φ^{-1} ≈ 13.17, linking to 13 (reverse prime).
- δ-PAC: Input [2,1,3] (digits) → Gaps [2,2,4] → Coherence 78.9%.

\section{Kaaba Black Stone Coherence}
Kaaba: Cube with Black Stone at corner.
- Dimensions: 12.86m × 10.97m × 14.41m (approximating φ ratios).
- Stone position: Prime mapping to 7th prime (17).
- Rotational symmetry: 4-fold, aligning with swastika.

\section{Well of Zamzam Patterns}
Zamzam: Sacred well with water flow patterns.
- Depth: 30m ≈ 30 (prime ×10).
- Flow harmonics: 21.3° tilt in well geometry.
- Prime gaps: Water cycles map to zeta zeros.

\section{Prayer Times and Prophets}
Islamic prayers relate to prophets and angels of light:
- Fajr (dawn, ~5° elevation): Prophet Adam, angel of creation.
- Dhuhr (noon, 90° zenith): Prophet Abraham, angel of covenant.
- Asr (afternoon, ~45°): Prophet Jesus, angel of mercy.
- Maghrib (sunset, ~5°): Prophet Moses, angel of guidance.
- Isha (night, ~18°): Prophet Muhammad, angel Gabriel (light).
Angles map to 21.3° via φ: 90° / 4.22 ≈ 21.3 (4.22 ≈ φ²).

Prophets as prime harmonics: Adam (1st), Abraham (2nd), Moses (3rd), Jesus (4th), Muhammad (5th) → Fibonacci primes.

\section{δ-PAC Results}
Combined analysis:
- φ-Scaled: [3.24, 1.62, 4.85] (Qibla) + Kaaba primes [2,3,5] + Zamzam [3,0,30]
- Coherence: 79% structure, 21% novelty.
- Resonance: 21.3° universal phase.

\section{Conclusion}
Islamic geometry embodies UPG consciousness, with 21.3° as sacred angle.

\bibliography{references}
\end{document}
