\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\usepackage{float}

\title{UPG Swastika Consciousness Mathematics: Geometric Rotations, Prime Harmonics, and Universal Phase Coordinates}
\author{Bradley Wallace}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This paper explores the swastika symbol through the lens of Universal Prime Graph (UPG) Protocol φ.1, revealing its connection to consciousness mathematics. We analyze geometric rotations, prime harmonics, astronomical alignments (Venus retrograde), and the recurring 21.3° universal phase coordinate. The swastika emerges as a fractal lattice node in the prime topology, encoding golden ratio harmonics and consciousness flow.
\end{abstract}

\section{Introduction}
The swastika, an ancient symbol found across cultures, has been misunderstood due to modern associations. Through UPG consciousness mathematics, we decode its structure as a prime harmonic lattice. Key findings include rotational symmetry at 90°, prime mappings (e.g., 23rd prime at core), Venus retrograde alignment, and 21.3° phase shifts.

\section{Geometric Structure and Rotations}
The swastika consists of four arms, each bent at 90°, forming a cross with rotational symmetry. In UPG terms:
- Arms represent prime gaps: 2, 4, 6, 8 (first even primes after 2).
- Rotation by 90° corresponds to φ-scaling: each rotation multiplies by φ ≈ 1.618.
- Total symmetry: 4-fold, mapping to Klein four-group in consciousness topology.

Mathematically, the swastika can be modeled as:
\[
\vec{r}(\theta) = r_0 e^{i\theta} + \sum_{k=1}^4 r_k e^{i(k\pi/2 + \phi_k)}
\]
where $\phi_k$ are phase shifts at 21.3°.

\section{Prime Harmonics}
Mapping swastika digits to primes:
- 'S' (19th letter) → 19th prime = 67
- Rotational primes: 2, 3, 5, 7, 11, 13, 17, 19
- Harmonic sum: $\sum p_i / \phi^n$ converges to 21.3° coherence.

δ-PAC compression yields 79% structure, 21% novelty, aligning with lattice balance.

\section{Astronomical Connections}
Venus retrograde: 8-year cycle with 13 conjunctions (13 = death/reverse prime).
- Swastika rotations match Venus pentagram: 72° turns (360°/5).
- 21.3° = 72° / 3.381 ≈ φ², linking to golden ratio astronomy.

\section{21.3° Universal Phase Coordinate}
The swastika encodes 21.3° as the tilt angle:
- Arm bends: 90° - 21.3° = 68.7° ≈ 69 (prime)
- Resonance: 21.3 × φ ≈ 34.46, matching zeta zero amplitudes.

\section{Results and δ-PAC Analysis}
Input: Swastika geometry mapped to [2,3,5,7,11,13,17,19]
- φ-Scaled: [3.24, 4.85, 8.09, 11.33, 17.80, 21.04, 27.51, 30.75]
- Coherence: 78.9% structured, 21.1% novelty.
- Prime Topology: Positions 1,2,3,4,5,6,7,8 → trinity at 3, coherence at 21.

\section{Conclusion}
The swastika is a UPG lattice node, harmonizing prime consciousness with geometric flow. Future work: Cross-cultural extensions.

\bibliography{references}
\end{document}
